Globally-centered autocovariances in MCMC

### 2020-07-23 Paper/main.tex
I lied. Some more for today. Ab bas.

Recall from Equation \ref{eq:empirical_acf} that $\hat{\Gamma}(k)$ is the empirical autocovariance function given by

\begin{equation}
    \hat{\Gamma}(k) = \dfrac{1}{n}\sum_{t=1}^{n-\abs{k}}(X_t - \bar{X})(X_{t + \abs{k}} - \bar{X})^T
\end{equation}

The spectral variance estimator is the weighted and truncated sum of lag-k autocovariances, given by:

\begin{equation} \label{eq:sve}
    \hat{\Sigma}_{SV} = \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_n(k)
\end{equation}

where $w(.)$ is the lag window and $b_n$ is the truncation point. Consider $m$ Markov chains where $\hat{\Gamma}_s(k)$, $\hat{\Gamma}_{G,s}(k)$ and $\hat{\Sigma}_{S, s}$ are the lag-$k$ empirical ACF, G-ACF, and SVE respectively for $s^{th}$ Markov chain, $s\in {1,...,m}$. We construct the globally-centered SVE estimator $\hat{\Sigma}_{G}$ using the globally-centered ACF. Consider, 
%
\begin{align*}
    \hat{\Sigma}_{G,s} &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_{G,s}(k)
\end{align*}
\[
\hat{\Sigma}_{G} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{G,s}
\]

@@

\begin{ass} \label{ass:sve_consis} We assume that all the conditions given by \cite{vats:fleg:jon:2018} for strong consistency of the spectral variance estimator hold true. As a consequence, 
\[
\hat{\Sigma}_{S,s} \xrightarrow{a.s.} \Sigma \textrm{ as } n \to \infty \;\; \forall s \in \{1,..., m\}
\]
\end{ass}

>>>>

% Recall from Equation \ref{eq:empirical_acf} that $\hat{\Gamma}(k)$ is the empirical autocovariance function given by

% \begin{equation}
%     \hat{\Gamma}(k) = \dfrac{1}{n}\sum_{t=1}^{n-\abs{k}}(X_t - \bar{X})(X_{t + \abs{k}} - \bar{X})^T
% \end{equation}

Let $w_n: \mathbb{R} \to [-z,z]$ be a lag window function and let $b_n \in \mathbb{N}$ be a truncation point. The usual SV estimator is the weighted and truncated sum of lag-$k$ autocovariances:
\begin{equation} \label{eq:sve}
    \hat{\Sigma}_{SV} = \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_n(k)
\end{equation}

% Consider $m$ Markov chains where $\hat{\Gamma}_s(k)$, $\hat{\Gamma}_{G,s}(k)$ and $\hat{\Sigma}_{S, s}$ are the lag-$k$ empirical ACF, G-ACF, and SVE respectively for $s^{th}$ Markov chain, $s\in {1,...,m}$. 
Consider the globally-centered SV estimator (G-SVE) for the $s$th chain using G-ACF:
%
\begin{align*}
    \hat{\Sigma}_{G,s} &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_{G,s}(k)\,,
\end{align*}
and the combined G-SVE is
\[
\hat{\Sigma}_{G} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{G,s}\,.
\]

@@

\begin{ass} \label{ass:sve_consis} We assume that all the conditions given by \cite{vats:fleg:jon:2018} for strong consistency of the spectral variance estimator hold true. As a consequence, $\hat{\Sigma}_{S,s} \xrightarrow{a.s.} \Sigma$ as $n \to \infty$ for all Markov chains $s$.
% \[
% \hat{\Sigma}_{S,s} \xrightarrow{a.s.} \Sigma \textrm{ as } n \to \infty \;\; \forall s \in \{1,..., m\}
% \]
\end{ass}
